---
title: "ETC1010-5510 Project - T11_Wed_skimr"
subtitle: "A Report On The LinkedIn-World Bank Data for Development"
author: "Hanchen Wang 30704456, Hao Li 32041594, Jiaying Zhang 30930685, Mohammed Faizan 31939872, Karan Garg 32106580"
date: "28 April 2021"
output: 
  bookdown::html_document2
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

#loading packages

library(tidyverse) 
library(plotly)
library(naniar)
library(visdat)
library(bookdown)
library(knitr)
library(ggplot2)
library(lubridate)
library(geosphere)
library(ggmap)
library(ggthemes)
library(maps)
library(patchwork)
library(here)
library(readxl)
```

#QUESTIONS

Q1) Which skill category is most common across all Industry Sections and how does it vary between each section? **(Hao Li)**

Q2) What is the average percentage of net migration for each industry over the past five years and is the growth rate of immigration within the industry related to the growth rate of the industry? **(Jiaying Zhang)**

Q3) For each industry_section, which industry has the highest penetration rate for the most common skill_category? **((Hanchen Wang)**

Q4) Find the industry_section that is best to each region/continent. **(Faizan & Karan)**

Q5) Which industry_name sees the maximum growth over time in each region/continent , depending on the region’s best industry_section ? **(Mohammed Faizan)**

# EDA

```{r reading_data}

skills_raw <- read_excel(here::here('data/1_skills.xlsx'), sheet=4)
penetration_raw <- read_excel(here::here('data/2_skill_penetration.xlsx'), sheet=4)
emp_growth_raw <- read_excel(here::here('data/3_employment_growth.xlsx'), sheet=4)


```

```{r}
# tidy emp_growth_raw

temp <- emp_growth_raw %>% select(starts_with("growth")) %>% names()
emp_growth_raw_long <- emp_growth_raw %>%
                          pivot_longer(cols = all_of(temp), 
                                       names_to = "year", 
                                       values_to = "growth_rate") %>%
                      separate(year, into = c("temp1","temp2","year"), convert = TRUE) %>%
                      select(-starts_with("temp"))
head(emp_growth_raw)
```

```{r}
#some summaries
#joining skills and penetration data

skill_penetration_common <- skills_raw %>%
                            inner_join(penetration_raw,
                                       by=c("year"="year",
                                          "isic_section_index"="isic_section_index",
                                       "isic_section_name"="isic_section_name",
                                       "skill_group_category"="skill_group_category",
                                       "skill_group_name"="skill_group_name",
                                       "industry_name"="industry_name")
                                       ) %>%
                            select(-isic_section_index)

#some summaries
unique(skill_penetration_common$year)
unique(skill_penetration_common$isic_section_name)
unique(skill_penetration_common$skill_group_category)

#all skills required by all industries except for mining and quarrying which does not require disruptive tech skills. soft skills importance remains same across industy sections.
skill_penetration_common%>%ggplot()+geom_count(mapping = aes(x=isic_section_name,skill_group_category))+theme(axis.text.x = element_text(angle = 60))
```

```{r }

industry_info <- skill_penetration_common %>% select(isic_section_name,industry_name) %>%
                  group_by(isic_section_name) %>% count(industry_name) %>% select(-n) %>%
                  ungroup()

industries <- industry_info%>%pivot_wider(id_cols= c(isic_section_name, industry_name), names_from = isic_section_name, values_from = industry_name)
industry_info%>%ggplot()+geom_bar(aes(x=isic_section_name))+coord_flip()+labs(title = "Industry Count within each Section")
```

```{r}

skills_info <- skill_penetration_common %>% select(skill_group_category,skill_group_name) %>%
                  group_by(skill_group_category) %>% count(skill_group_name) %>% select(-n) %>%
                  ungroup()
skills <- skills_info%>%pivot_wider(id_cols= c(skill_group_category, skill_group_name), names_from = skill_group_category, values_from = skill_group_name)
skills_info%>%ggplot()+geom_bar(aes(x=skill_group_category))+coord_flip()+labs(title = "Skill Count within each Skill Category")
```

```{r eda_emp_growth}
pct_miss(emp_growth_raw_long) #no missingness
length(unique(emp_growth_raw_long$country_name))
unique(emp_growth_raw_long$wb_region)
unique(emp_growth_raw_long$wb_income)
unique(emp_growth_raw_long$isic_section_name)
unique(emp_growth_raw_long$year)

```

```{r}

gfun <- function(x){
  temp <- emp_growth_raw_long%>%filter(year==x)
  return(temp)
}
emp_growth_yearwise <- list(gfun(2015),gfun(2016),gfun(2017),gfun(2018),gfun(2019))

```


```{r}
#for each region, every year there same number of records for each industry_section
emp_growth_raw_long%>%count(wb_region,isic_section_name,year)%>%pivot_wider(id_cols = c(year,n,wb_region,isic_section_name),names_from = year, values_from=n)

emp_growth_raw_long%>%count(wb_region,isic_section_index,year)%>%ggplot()+geom_col(mapping = aes(x=isic_section_index,y=n,fill=as.character(year)),position ="dodge")+facet_wrap(~wb_region)#+theme(axis.text.x = element_blank())

#presence of industries in each region
emp_growth_raw_long %>%
  ggplot()+geom_count(mapping=aes(x=wb_region, y=isic_section_name))+theme(axis.text.x = element_text(angle = 45))



```


Q6) For each region, which country did the above found industry had had maximum growth? And, what is the income group of that nation? **(Karan Garg)**

