---
title: "ETC1010-5510 Project - T11_Wed_skimr"
subtitle: "A Report On The LinkedIn-World Bank Data for Development"
author: "Hanchen Wang 30704456, Hao Li 32041594, Jiaying Zhang 30930685, Mohammed Faizan 31939872, Karan Garg 32106580"
date: "28 April 2021"
output: 
  bookdown::html_document2
keep_md: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

#loading packages

library(tidyverse) 
library(plotly)
library(naniar)
library(visdat)
library(bookdown)
library(knitr)
library(ggplot2)
library(lubridate)
library(geosphere)
library(ggmap)
library(ggthemes)
library(maps)
library(patchwork)
library(here)
library(readxl)
library(readr)
```
#QUESTIONS

1) **Which skill category is most common across all Industry Sections and how does it vary between each section?**

2) **What is the average percentage of net migration for each industry over the past five years and Is the growth rate of immigration within the industry related to the growth rate of the industry?**
```{r read-data}
mgindustry <- read_csv(here::here("data/migration_industry.csv"))
growindustry<- read_csv(here::here("data/3_employment_growth.csv"))
```
```{r datacleaning, include=FALSE}
mgpick <- mgindustry %>% 
  select(industry_name,
         industry_id,
         isic_section_index,
         isic_section_name,
                net_per_10K_2015,
                net_per_10K_2016,
                net_per_10K_2017,
                net_per_10K_2018,
                net_per_10K_2019)
growpick <- growindustry %>% 
  select(industry_name, 
         industry_id,
                growth_rate_2015,
                growth_rate_2016,
                growth_rate_2017,
                growth_rate_2018,
                growth_rate_2019)

```
#average percentage of net migration for each industry over the past five years

```{r mgdatause}
mguse<- mgpick %>% 
   rename(c("2015"= "net_per_10K_2015",
           "2016"= "net_per_10K_2016",
           "2017"= "net_per_10K_2017",
           "2018"= "net_per_10K_2018",
           "2019"= "net_per_10K_2019",
           "industry" = "industry_name",
           "industry_section"= "isic_section_index",
           "section_name" = "isic_section_name")) %>% 
    pivot_longer(cols = 5:9,  
               names_to = "year",            
               values_to = "net_migration_rate") %>% 
 mutate(migration_year= year,
        migration_industry_id = industry_id) %>% 
 unite("industry_year", migration_industry_id, year)
```
```{r mgave}
mgave <- mguse %>% 
  group_by(industry_year) %>% 
  summarise(average_migration_rate = mean(net_migration_rate, na.rm = TRUE),
            industry_section_index = industry_section) 
```
```{r mgfinal}
mgfinal <- mgave %>% separate(industry_year,
           c("industry","year"), "_") %>% 
  mutate(year = as.numeric(year)) %>% 
  group_by(industry_section_index)
```

#Is the growth rate of immigration within the industry related to the growth rate of the industry?

```{r relationdata}
growuse <- growpick %>% 
   rename(c("2015"= "growth_rate_2015",
           "2016"= "growth_rate_2016",
           "2017"= "growth_rate_2017",
           "2018"= "growth_rate_2018",
           "2019"= "growth_rate_2019"
           )) %>% 
    pivot_longer(cols = 3:7,  
               names_to = "year",            
               values_to = "growth_rate") %>% 
 unite("industry_year", industry_id, year)
growclean <- growuse %>% 
  mutate(growth_rate = str_sub(growuse$growth_rate,start = 1, end = -2))%>% 
  mutate(growth_rate = as.numeric(growth_rate)) %>% 
  na.omit()
```

```{r growave}
growave <- growclean %>% 
  group_by(industry_year) %>% 
summarise(average_grow_rate = mean(growth_rate, na.rm = TRUE))
```
```{r full}
fulldata<- mgave %>% 
  inner_join(growave, by="industry_year")
```

```{r finaldata}
cleandata <- fulldata %>% separate(industry_year,
           c("industry_section","year"), "_") %>% 
  mutate(year = as.numeric(year)) %>% 
  unique()
```

3) **For each industry_section, which industry has the highest penetration rate for the most common skill_category?**

4) **Find the industry_section that is best to each region/continent.**

5) **Which industry_name sees the maximum growth over time in each region/continent , depending on the region’s best industry_section?**

6) **For each region, which country did the above found industry had had maximum growth? And, what is the income group of that nation?**


