---
title: "ETC1010-5510 Project - T11_Wed_skimr"
subtitle: "A Report On The LinkedIn-World Bank Data for Development"
author: "Hanchen Wang 30704456, Hao Li 32041594, Jiaying Zhang 30930685, Mohammed Faizan 31939872, Karan Garg 32106580"
date: "28 April 2021"
output: 
  bookdown::html_document2
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

#loading packages

library(tidyverse) 
library(plotly)
library(naniar)
library(visdat)
library(bookdown)
library(knitr)
library(ggplot2)
library(lubridate)
library(geosphere)
library(ggmap)
library(ggthemes)
library(maps)
library(patchwork)
library(here)
library(readxl)
```

#QUESTIONS

1) **Which skill category is most common across all Industry Sections and how does it vary between each section?**

2) **How does the common skill category vary within and between industry_section according to the rank over the period of time?**

3) **For each industry_section, which industry has the highest penetration rate for the most common skill_category?**

4) **Find the industry_section that is best to each region/continent.**

5) **Which industry_name sees the maximum growth over time in each region/continent , depending on the region’s best industry_section?**

6) **For each region, which country did the above found industry had had maximum growth? And, what is the income group of that nation?**


# EDA

```{r reading_data}

skills_raw <- read_excel(here::here('data/1_skills.xlsx'), sheet=4)
penetration_raw <- read_excel(here::here('data/2_skill_penetration.xlsx'), sheet=4)
emp_growth_raw <- read_excel(here::here('data/3_employment_growth.xlsx'), sheet=4)


```

```{r}
# tidy emp_growth_raw

temp <- emp_growth_raw %>% select(starts_with("growth")) %>% names()
emp_growth_raw_long <- emp_growth_raw %>%
                          pivot_longer(cols = all_of(temp), 
                                       names_to = "year", 
                                       values_to = "growth_rate") %>%
                      separate(year, into = c("temp1","temp2","year"), convert = TRUE) %>%
                      select(-starts_with("temp"))
head(emp_growth_raw)
```

```{r}
#some summaries
#joining skills and penetration data

skill_penetration_common <- skills_raw %>%
                            inner_join(penetration_raw,
                                       by=c("year"="year",
                                          "isic_section_index"="isic_section_index",
                                       "isic_section_name"="isic_section_name",
                                       "skill_group_category"="skill_group_category",
                                       "skill_group_name"="skill_group_name",
                                       "industry_name"="industry_name")
                                       ) %>%
                            select(-isic_section_index)

#some summaries
unique(skill_penetration_common$year)
unique(skill_penetration_common$isic_section_name)
unique(skill_penetration_common$skill_group_category)

#all skills required by all industries except for mining and quarrying which does not require disruptive tech skills. soft skills importance remains same across industy sections.
skill_penetration_common%>%ggplot()+geom_count(mapping = aes(x=isic_section_name,skill_group_category))+theme(axis.text.x = element_text(angle = 60))

industry_info <- skill_penetration_common %>% select(isic_section_name,industry_name) %>%
                  group_by(isic_section_name) %>% count(industry_name) %>% select(-n) %>%
                  ungroup()

industries <- industry_info%>%pivot_wider(id_cols= c(isic_section_name, industry_name), names_from = isic_section_name, values_from = industry_name)
industry_info%>%ggplot()+geom_bar(aes(x=isic_section_name))+coord_flip()+labs(title = "Industry Count within each Section")

skills_info <- skill_penetration_common %>% select(skill_group_category,skill_group_name) %>%
                  group_by(skill_group_category) %>% count(skill_group_name) %>% select(-n) %>%
                  ungroup()
skills <- skills_info%>%pivot_wider(id_cols= c(skill_group_category, skill_group_name), names_from = skill_group_category, values_from = skill_group_name)
skills_info%>%ggplot()+geom_bar(aes(x=skill_group_category))+coord_flip()+labs(title = "Skill Count within each Skill Category")



```






